%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% %
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%

\begin{thebibliography}{99.}%

\bibitem{clifford2006advanced}
Gari~D Clifford, Francisco Azuaje, Patrick McSharry, et~al.
\newblock {\em Advanced methods and tools for ECG data analysis}.
\newblock Artech House, Boston, 2006.

\bibitem{ai1996studies}
HB~Ai, XY~Cui, L~Tang, WP~Zhu, XB~Ning, and XX~Yang.
\newblock [studies on the time domain and power spectrum of high frequency ecg
  in normal mice].
\newblock {\em Sheng li xue bao:[Acta physiologica Sinica]}, 48(5):512--516,
  1996.

\bibitem{andreao2006ecg}
Rodrigo~Varej{\~a}o Andre{\~a}o, Bernadette Dorizzi, and J{\'e}r{\^o}me Boudy.
\newblock Ecg signal analysis through hidden markov models.
\newblock {\em  IEEE Transactions on Biomedical Engineering}, 53(8):1541--1549,
  2006.

\bibitem{bengio2009learning}
Yoshua Bengio.
\newblock Learning deep architectures for ai.
\newblock {\em Foundations and trends{\textregistered} in Machine Learning},
  2(1):1--127, 2009.

\bibitem{bengio2007greedy}
Yoshua Bengio, Pascal Lamblin, Dan Popovici, Hugo Larochelle, et~al.
\newblock Greedy layer-wise training of deep networks.
\newblock {\em Advances in neural information processing systems}, 19:153,
  2007.

\bibitem{bishop2006pattern}
Christopher~M Bishop et~al.
\newblock {\em Pattern recognition and machine learning}, volume~4.
\newblock springer New York, 2006.

\bibitem{blanco2008ecg}
Manuel Blanco-Velasco, Binwei Weng, and Kenneth~E Barner.
\newblock Ecg signal denoising and baseline wander correction based on the
  empirical mode decomposition.
\newblock {\em Computers in biology and medicine}, 38(1):1--13, 2008.

\bibitem{clifford2006web}
Gari~D Clifford, Francisco Azuaje, and McScharry.
\newblock Advanced tools for ecg analysis, September 2006.

\bibitem{collobert}
Ronan Collobert and Jason Weston.
\newblock A unified architecture for natural language processing: Deep neural
  networks with multitask learning.
\newblock In {\em Proceedings of the 25th international conference on Machine
  learning}, pages 160--167. ACM, 2008.

\bibitem{de2004automatic}
Philip De~Chazal, Maria O'Dwyer, and Richard~B Reilly.
\newblock Automatic classification of heartbeats using ecg morphology and
  heartbeat interval features.
\newblock {\em  IEEE Transactions on Biomedical Engineering}, 51(7):1196--1206,
  2004.

\bibitem{duda2012pattern}
Richard~O Duda, Peter~E Hart, and David~G Stork.
\newblock {\em Pattern classification}.
\newblock John Wiley \& Sons, 2012.

\bibitem{erhan}
Dumitru Erhan, Pierre-Antoine Manzagol, Yoshua Bengio, Samy Bengio, and Pascal
  Vincent.
\newblock The difficulty of training deep architectures and the effect of
  unsupervised pre-training.
\newblock In {\em International Conference on Artificial Intelligence and
  Statistics}, pages 153--160, 2009.

\bibitem{gacek2003genetic}
Adam Gacek and Witold Pedrycz.
\newblock A genetic segmentation of ecg signals.
\newblock {\em  IEEE Transactions on Biomedical Engineering},
  50(10):1203--1208, 2003.

\bibitem{hinton2006reducing}
Geoffrey~E Hinton and Ruslan~R Salakhutdinov.
\newblock Reducing the dimensionality of data with neural networks.
\newblock {\em Science}, 313(5786):504--507, 2006.

\bibitem{mar2011optimization}
Tanis Mar, Sebastian Zaunseder, Juan~Pablo Martinez, Mariano Llamedo, and
  R{\"u}diger Poll.
\newblock Optimization of ecg classification by means of feature selection.
\newblock {\em IEEE Transactions on Biomedical Engineering}, 58(8):2168--2177,
  2011.

\bibitem{mark1982annotated}
RG~Mark, PS~Schluter, G~Moody, P~Devlin, and D~Chernoff.
\newblock An annotated ecg database for evaluating arrhythmia detectors.
\newblock In {\em IEEE Transactions on Biomedical Engineering}, volume~29,
  pages 600--600, 1982.

\bibitem{moody1990bih}
George~B Moody and Roger~G Mark.
\newblock The mit-bih arrhythmia database on cd-rom and software for use with
  it.
\newblock In {\em Computers in Cardiology 1990, Proceedings.}, pages 185--188,
  1990.

\bibitem{ufldl}
Andrew Ng, Jiquan Ngiam, Chuan~Y. Foo, Yifan Mai, and Caroline Suen.
\newblock {UFLDL Tutorial}.
\newblock {\em http://ufldl.stanford.edu/}, 2010.

\bibitem{ngiam2011optimization}
Jiquan Ngiam, Adam Coates, Ahbik Lahiri, Bobby Prochnow, Quoc~V Le, and
  Andrew~Y Ng.
\newblock On optimization methods for deep learning.
\newblock In {\em Proceedings of the 28th International Conference on Machine
  Learning (ICML-11)}, pages 265--272, 2011.

\bibitem{sayadi2009model}
O~Sayadi and MB~Shamsollahi.
\newblock A model-based bayesian framework for ecg beat segmentation.
\newblock {\em Physiological Measurement}, 30(3):335, 2009.

\bibitem{silva2011dsp}
Cristian~Vidal Silva, Andrew Philominraj, and Carolina del R{\'\i}o.
\newblock {\em A DSP Practical Application: Working on ECG Signal}.
\newblock INTECH Open Access Publisher, 2011.

\bibitem{vullings1998automated}
HJLM Vullings, MHG Verhaegen, and H~Verbruggen.
\newblock Automated ecg segmentation with dynamic time warping.
\newblock In {\em Engineering in Medicine and Biology Society, 1998.
  Proceedings of the 20th Annual International Conference of the IEEE}, pages
  163--166. IEEE, 1998.

\bibitem{vullings1997ecg}
HJLM Vullings, MHG Verhaegen, and Henk~B Verbruggen.
\newblock Ecg segmentation using time-warping.
\newblock In {\em Advances in Intelligent Data Analysis Reasoning about Data},
  pages 275--285. Springer, 1997.

\bibitem{zigel2000weighted}
Yaniv Zigel, Arnon Cohen, and Amos Katz.
\newblock The weighted diagnostic distortion (wdd) measure for ecg signal
  compression.
\newblock {\em  IEEE Transactions on Biomedical Engineering},
  47(11):1422--1430, 2000.

\bibitem{zou2012deep}
Will Zou, Shenghuo Zhu, Kai Yu, and Andrew~Y Ng.
\newblock Deep learning of invariant features via simulated fixations in video.
\newblock In {\em Advances in Neural Information Processing Systems}, pages
  3212--3220, 2012.



\end{thebibliography}
